Precision calculations for cosmic shear

### 2017-02-09 cfhtlens.tex
Added author list, addresses and the acks that I know about
Centered Tab 2 Updated reference in Fig 2 (Planck referenced twice previously)

For a first-order standard Limber flat-sky approximation (L1Fl) we find
$\sigma_8 (\Omega_{\rm m}/0.27)^{0.6} =0.787^{+0.031}_{-0.033}$, the same
result that was published in \cite{CFHTLenS-2pt-notomo}. Using the second-order
extended Limber flat-sky approximation results in $\sigma_8 (\Omega_{\rm
m}/0.27)^{0.6} =X^{+X}_{-X}$, a negligible change of $X\sigma$.

@@

\renewcommand{\baselinestretch}{1.5}
\begin{table}

  \label{tab:CFHTLenS_Sigma8}

@@

\end{table}
\renewcommand{\baselinestretch}{1}

>>>>

For a first-order standard Limber flat-sky approximation (L1Fl) we find
$\sigma_8 (\Omega_{\rm m}/0.27)^{0.6} =0.787^{+0.031}_{-0.033}$, the same
result that was published in \cite{CFHTLenS-2pt-notomo}. Using the second-order
extended Limber flat-sky approximation results in \ch{$\sigma_8 (\Omega_{\rm
m}/0.27)^{0.6} =X^{+X}_{-X}$}, a negligible change of $X\sigma$.

@@

\renewcommand{\baselinestretch}{1.5}
\begin{table}
\begin{centering}
  \label{tab:CFHTLenS_Sigma8}

@@

\end{centering}
\end{table}
\renewcommand{\baselinestretch}{1}

### 2017-02-09 limber2.tex
Centered Tab 2 Updated reference in Fig 2 (Planck referenced twice previously)

  \caption{Shear correlation functions $\xi_+$ (\emph{left}) and $\xi_-$ (\emph{right}).
    The lower panels shows the relative differences to the case ExtL2Sph,  see Table \ref{tab:cases} for the different
    approximations and their symbols.
    The theoretical model corresponds to the CFHTLenS best-fit parameters with
    $\Omega_{\rm m} = 0.279$, $h=0.701$, and $\sigma_8 = 0.79$ \citep{2015arXiv150201589P},
    except the red dashed curve with adapts a Planck-best fit
    cosmology with $\Omega_{\rm m} = 0.3$, $h=0.67$ and $\sigma_8 = 0.83$ \citep{2015arXiv150201589P}.
  }

>>>>

  \caption{Shear correlation functions $\xi_+$ (\emph{left}) and $\xi_-$ (\emph{right}).
    The lower panels shows the relative differences to the case ExtL2Sph,  see Table \ref{tab:cases} for the different
    approximations and their symbols.
    The theoretical model corresponds to the CFHTLenS best-fit parameters with
    $\Omega_{\rm m} = 0.279$, $h=0.701$, and $\sigma_8 = 0.79$ \citep{CFHTLenS-2pt-notomo},
    except the red dashed curve with adapts a Planck-best fit
    cosmology with $\Omega_{\rm m} = 0.3$, $h=0.67$ and $\sigma_8 = 0.83$ \citep{2015arXiv150201589P}.
  }
